Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-08-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
added references

In this chapter the application of emprical algebraic fire characterizations will be examined. Two different types of applications will be used.  In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.  In the second case, the height of the thermal damage on the gypsum board will be examined.

Values generated in the bench scale experiments will be utilized as input to predict real scale results using the algorithms.  Then the predicted results will be compared with the full-scale experimental results.

@@

Ratio from heat flux from source fire data
vyto second item ignite
\begin{equation} \label{eq:second_item}
\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
\end{equation}

@@

discuss the premise
McCaffery

>>>>

In this chapter the application of emprical algebraic fire characterizations will be examined. Two different types of applications will be used.  In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.  In the second case, the height of the thermal damage on the gypsum board will be examined.  
Applications of algorithms such as these are presented in cureent fire investigaton textbooks~\cite{Icove:2013}.

Values generated in the bench scale experiments will be utilized as input to predict or simulate real scale results using the algorithms.  Then the predicted results will be compared with the full-scale experimental results.

@@

The first              ~\cite{Babrauskas:1981}

Ratio from heat flux from source fire data
vyto second item ignite

\begin{equation} \label{eq:second_item}
\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
\end{equation}

@@

discuss the premise    ~\cite{McCaffrey:1979}
McCaffery
